Modal type theory based on the intuitionistic epistemic logic

### 2018-02-10 article.tex
updated definitions and lemmas

Also we accept the following equality, so called symmetricity of local binding:

\begin{defin} Symmetricity of local binding

  ${\bf let \: pure \:} \vec{x}, \vec{y} = \vec{M}, \vec{N} {\: \bf in \:} P \equiv {\bf let \: pure \:} \vec{y}, \vec{x} = \vec{N}, \vec{M} {\: \bf in \:} P$

@@

\begin{prop}

  If $\Gamma \vdash {\bf let \: pure \:} \vec{x}, \vec{y} = \vec{M}, \vec{N} {\: \bf in \:} P : {\bf K}A$, then
  $\Gamma \vdash {\bf let \: pure \:} \vec{y}, \vec{x} = \vec{N}, \vec{M} {\: \bf in \:} P : {\bf K}A$.
\end{prop}

  Follows from the part 5 of the previous lemma.
\end{proof}

@@

@@

3) Weak commutativity condition:

\xymatrix{
&& A \otimes \mathcal{K}B \ar[d]_{\sigma_{A, \mathcal{K}B}} \ar[rr]^{\eta_{A} \otimes id_{\mathcal{K}B}} && \mathcal{K}A \otimes \mathcal{K}B \ar[rr]^{\ast_{A,B}} && \mathcal{K}(A \otimes B) \ar[d]^{\mathcal{K}(\sigma_{A,B})}\\
&& \mathcal{K}B \otimes A \ar[rr]_{id_{\mathcal{K}B} \otimes \eta_{A}} && \mathcal{K}B \otimes \mathcal{K}A \ar[rr]_{\ast_{B,A}} && \mathcal{K}(B \otimes A)
}
\end{defin}

@@

\begin{prop}
$ $

  $[\![\Gamma \vdash {\bf let \: pure \:} \vec{x}, \vec{y} = \vec{M}, \vec{N} {\: \bf in \:} P : {\bf K} C]\!] = [\![\Gamma \vdash {\bf let \: pure \:} \vec{y}, \vec{x} = \vec{N}, \vec{M} {\: \bf in \:} P : {\bf K} C]\!]$
\end{prop}

  Follows from the commutativity of the following diagram:

\xymatrix{
[\![\Gamma]\!] \ar[rr]^{\langle g, f \rangle} \ar[d]_{\langle f, g \rangle} && \mathcal{K}[\![B]\!] \times \mathcal{K}[\![A]\!] \ar[rr]^{\ast_{[\![B]\!], [\![A]\!]}}
\ar[d]_{\ast_{[\![A]\!], [\![B]\!]} \circ \langle \pi_2, \pi_1 \rangle} && \mathcal{K}([\![B]\!] \times [\![A\!]) \ar[d]^{\mathcal{K}{[\![N]\!]} \circ \mathcal{K}(\langle \pi_2, \pi_1 \rangle)} \\
\mathcal{K}[\![A\!] \times \mathcal{K}[\![B]\!] \ar[rr]_{\ast_{[\![A]\!], [\![B]\!]}} && \mathcal{K}([\![A]\!] \times [\![B]\!]) \ar[rr]_{[\![N]\!]}&& \mathcal{K}[\![C]\!]
}

@@

\begin{lemma} Weak commutativity.
  $ $

  $\begin{array}{lll}
  & \text{fmap } ([p, \langle \pi_2 p, \pi_1 p \rangle]) \circ \tau_{\hat{A},\hat{B}} = & \\
  & \ast_{\hat{B}, \hat{A}} \circ [q, \langle \pi_1 q, {\bf pure \:} (\pi_2 q) \rangle] \circ [p, \langle \pi_2 p, \pi_1 p \rangle]&
  \end{array}$
\end{lemma}

@@

  $\begin{array}{lll}
  & \text{fmap } ([r, \langle \pi_2 r, \pi_1 r \rangle]) \circ \tau_{\hat{A},\hat{B}} = & \\
  &\text{By the definition of $\tau$}& \\
  & \text{fmap } ([r, \langle \pi_2 r, \pi_1 r \rangle]) \circ [p, {\bf let \: pure \:} x, y = {\bf pure \:} (\pi_1 p), \pi_2 p {\: \bf in \:} \langle x, y \rangle] = & \\
  &\text{By the definition of fmap}& \\
  & [q, {\bf let \: pure \:} r = q {\: \bf in \:} \langle \pi_2 r, \pi_1 r \rangle] \circ [p, {\bf let \: pure \:} x, y = {\bf pure \:} (\pi_1 p), \pi_2 p {\: \bf in \:} \langle x, y \rangle] = & \\
  &\text{Composition}& \\
  & [p, {\bf let \: pure \:} r = q {\: \bf in \:} \langle \pi_2 r, \pi_1 r \rangle [q := {\bf let \: pure \:} x, y = {\bf pure \:} (\pi_1 p), \pi_2 p {\: \bf in \:} \langle x, y \rangle]] = &\\
  &\text{By $\beta$-reduction rules}& \\
  & [p, {\bf let \: pure \:} r = ({\bf let \: pure \:} x, y = {\bf pure \:} (\pi_1 p), \pi_2 p {\: \bf in \:} \langle x, y \rangle) {\: \bf in \:} \langle \pi_2 r, \pi_1 r \rangle] = & \\
  &\text{By $\beta$-reduction rules}& \\
  & [p, {\bf let \: pure \:} x, y = {\bf pure \:} (\pi_1 p), \pi_2 p {\: \bf in \:} \langle \pi_2 r, \pi_1 r \rangle [r := \langle x, y \rangle]] = & \\
  &\text{By substitution}& \\
  & [p, {\bf let \: pure \:} x, y = {\bf pure \:} (\pi_1 p), \pi_2 p {\: \bf in \:} \langle \pi_2 \langle x, y \rangle, \pi_1 \langle x, y \rangle \rangle]= & \\
  &\text{By $\beta$-reduction rules}& \\
  & [p, {\bf let \: pure \:} x, y = {\bf pure \:} (\pi_1 p), \pi_2 p {\: \bf in \:} \langle y, x \rangle ] = & \\
  & & \\
  &\text{On the other hand}&\\
  &\ast_{\hat{B}, \hat{A}} \circ [q, \langle \pi_1 q, {\bf pure \:} (\pi_2 q) \rangle] \circ [p, \langle \pi_2 p, \pi_1 p \rangle] = & \\
  &\text{By the definition of $\ast$}& \\
  &[r, {\bf let \: pure \:} y,x = \pi_1 r, \pi_2 r {\: \bf in \:} \langle y, x \rangle] \circ [q, \langle \pi_1 q, {\bf pure \:} (\pi_2 q) \rangle] \circ [p, \langle \pi_2 p, \pi_1 p \rangle] = & \\
  &\text{Composition}& \\
  &[r, {\bf let \: pure \:} y,x = \pi_1 r, \pi_2 r {\: \bf in \:} \langle y, x \rangle] \circ [p, \langle \pi_1 q, {\bf pure \:} (\pi_2 q) \rangle [q := \langle \pi_2 p, \pi_1 p  \rangle]] = & \\
  &\text{By subsitution and by  $\beta$-reduction rules}& \\
  &[r, {\bf let \: pure \:} y,x = \pi_1 r, \pi_2 r {\: \bf in \:} \langle y, x \rangle] \circ [p, \langle \pi_2 p, {\bf pure \:} (\pi_1 p) \rangle ]] = & \\
  &\text{Composition}& \\
  &[p, {\bf let \: pure \:} y,x = \pi_1 r, \pi_2 r {\: \bf in \:} \langle y, x \rangle [r := \langle \pi_2 p, {\bf pure \:} (\pi_1 p) \rangle]] = & \\
  &\text{By subsitution and by  $\beta$-reduction rules}& \\
  &[p, {\bf let \: pure \:} y,x = \pi_2 p, {\bf pure \:} (\pi_1 p) {\: \bf in \:} \langle y, x \rangle] = & \\
  &\text{By symmetricity of assingment}&\\
  &[p, {\bf let \: pure \:} x,y = {\bf pure \:} (\pi_1 p), \pi_2 p {\: \bf in \:} \langle y, x \rangle]&
  \end{array}$
\end{proof}

>>>>

@@

@@

Strong endofunctor on a monoidal category is a with a natural transformation so called tensorial strength

\begin{equation}
  \tau_{A, B} : A \otimes \mathcal{K}B \rightarrow \mathcal{K}(A \otimes B)
\end{equation}

making two diagrams commute:

\xymatrix{
(A \otimes B) \otimes \mathcal{K}C \ar[d]_{\alpha_{A, B, \mathcal{K}C}}\ar[rrrr]^{\tau_{A \otimes B, C}} &&&& \mathcal{K}((A \otimes B) \otimes C) \ar[d]^{\mathcal{K}(\alpha_{A,B,C})}\\
A \otimes (B \otimes \mathcal{K}C) \ar[rr]_{id_A \otimes \tau_{B,C}} && A \otimes \mathcal{K}(B \otimes C) \ar[rr]_{\quad \tau_{A, (B \otimes C)}} && \mathcal{K}(A \otimes (B \otimes C)) \\
}

\xymatrix{
&&& \mathds{1} \otimes \mathcal{K}A \ar[drr]_{\rho_{\mathcal{K}A}} \ar[rr]^{\mu_{\mathds{1}, A}} && \mathcal{K}(\mathds{1} \otimes A) \ar[d]^{\mathcal{K}(\rho_A)}\\
&&&&& \mathcal{K}A
}
\end{defin}

@@

3) $\tau_{A, B} = \ast_{A, B} \circ \eta_{A} \otimes id_{\mathcal{K}B}$.
\end{defin}

@@

@@

\begin{lemma} Coherence for tensorial strength

  \begin{itemize}
    \item $\text{fmap } \alpha_{\hat{A},\hat{B},\hat{C}} \circ \tau_{\hat{A} \times \hat{B}, \hat{C}} = \tau_{\hat{A}, \hat{B} \times \hat{C}} \circ (id_{\hat{A}} \times \tau_{\hat{B}, \hat{C}}) \circ \alpha_{\hat{A}, \hat{B}, {\bf K}\hat{C}}$;
    \item ${\bf K}(\rho_{\hat{A}}) \circ \tau_{\mathds{1}, \hat{A}} = \rho_{{\bf K}\hat{A}}$.
  \end{itemize}
  where $\alpha_{\hat{A},\hat{B},\hat{C}} = [p, \langle \pi_1 (\pi_1 p), \langle \pi_1 (\pi_2 p), \pi_2 p \rangle \rangle]$ and
  $\rho = \pi_2$.
\end{lemma}

@@

Routine checking.
\end{proof}
